### 2022-06-13 paper.tex
removed todos

Lukas P.~M. Kremer\textsuperscript{1,2,*}, Leonie Küchenhoff\textsuperscript{1,2}, Santiago Cerrizuela\textsuperscript{2}, \todo{...}, Ana Martin-Villalba\textsuperscript{2}, Simon Anders\textsuperscript{1,*}\\[1ex]
{\footnotesize \textsuperscript{1} BioQuant Centre, University of Heidelberg, Heidelberg, Germany\\[-.5ex]
\textsuperscript{2} Molecular Neurobiology Dept., German Cancer Research Center (DKFZ), Heidelberg, Germany}
\vspace{1.5ex}

@@

To assess the impact of our methods on dimensionality reduction and the ability to distinguish different (sub)types of cells, we used a data set from \citet{luo2017single}. This data set consists of 3377 single-cell CpG methylomes from the murine frontal cortex, comprising 16 neuronal subtypes.
We subjected this data set to the standard scBS workflow: defining a set of genomic intervals, quantifying methylation in these intervals, and subjecting the resulting matrix to PCA.
We repeated this analysis several times, either using 100~kb tiles or VMRs, and either using methylation fractions or mean shrunken residuals as a measure of methylation. \todo{Is the following correct?} For both types of regions, the 100~kb tiles and the VMRs, we ranked the regions by the number of covering cells (i.e., cells with at least on read in the region) and kept only the top 100, 1000, or 10,000 regions.

>>>>

Lukas P.~M. Kremer\textsuperscript{1,2,*}, Leonie Küchenhoff\textsuperscript{1,2}, Santiago Cerrizuela\textsuperscript{2}, Ana Martin-Villalba\textsuperscript{2}, Simon Anders\textsuperscript{1,*}\\[1ex]
{\footnotesize \textsuperscript{1} BioQuant Centre, University of Heidelberg, Heidelberg, Germany\\[-.5ex]
\textsuperscript{2} Molecular Neurobiology Dept., German Cancer Research Center (DKFZ), Heidelberg, Germany}
\vspace{1.5ex}

@@

To assess the impact of our methods on dimensionality reduction and the ability to distinguish different (sub)types of cells, we used a data set from \citet{luo2017single}. This data set consists of 3377 single-cell CpG methylomes from the murine frontal cortex, comprising 16 neuronal subtypes.
We subjected this data set to the standard scBS workflow: defining a set of genomic intervals, quantifying methylation in these intervals, and subjecting the resulting matrix to PCA.
We repeated this analysis several times, either using 100~kb tiles or VMRs, and either using methylation fractions or mean shrunken residuals as a measure of methylation. For both types of regions, the 100~kb tiles and the VMRs, we ranked the regions by the number of covering cells (i.e., cells with at least on read in the region) and kept only the top 100, 1000, or 10,000 regions.
